Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-06 testbed.tex
testbed

\begin{lstlisting}[]
# (echo d; echo ; echo n; echo p; echo ; echo 137216; echo ; echo p; echo w) | fdisk ${IMAGE}.img
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Make the Raspbian image available as a block device: 
\begin{lstlisting}[]
# DEV=$(losetup --show -f -P ${IMAGE}.img); echo $DEV
/dev/loop0
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

Finally, to actually make the \ac{Raspi}s change hostname, we have to make
each \ac{Raspi} call the above script when it starts up.
Do this by inserting the line below in "\$\{ROOTDIR\}/etc/rc.local".
The file
can be opened with your favorite text editor.

\begin{lstlisting}[]
bash /home/pi/rasp_config/set_hostname"
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

% CHROOT to OS image
\begin{lstlisting}[]
# cd $ROOTDIR
# cp /etc/resolv.conf etc/resolv.conf
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

% Exit chroot, umount, and write to memory card
\begin{lstlisting}[]
# exit
# cd ..
# umount --recursive ${ROOTDIR}
# losetup -d ${DEV}.img
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

>>>>

\begin{lstlisting}[]
$ (echo d; echo ; echo n; echo p; echo ; echo 137216; echo ; echo p; echo w) | fdisk ${IMAGE}.img
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

Make the Raspbian image available as a block device (notice that the
command is run as root using sudo): 
\begin{lstlisting}[]
# export DEV=$(sudo losetup --show -f -P ${IMAGE}.img); echo $DEV
/dev/loop0
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

Finally, to actually make the \ac{Raspi}s change hostname, we have to make
each \ac{Raspi} call the above script when it starts up.
Do this with root permissions by inserting the line before
\texttt{"exit 0"} using your favorite editor:
%"\$\{ROOTDIR\}/etc/rc.local" using
%your favorite text editor..
%The file
%can be opened with your favorite text editor.

\Suppressnumber\begin{lstlisting}[]
<@\textcolor{gray}{\$\{ROOTDIR\}/etc/rc.local}@>
<@\textcolor{gray}{
-----------------------------------------------------}
\Reactivatenumber @>
...
bash /home/pi/rasp_config/set_hostname
...
exit 0
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

% CHROOT to OS image
\begin{lstlisting}[]
$ cd $ROOTDIR
# cp /etc/resolv.conf etc/resolv.conf
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

@@

% Exit chroot, umount, and write to memory card
\begin{lstlisting}[]
# exit
# cd ..
# umount --recursive ${ROOTDIR}
# losetup -d ${DEV}
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}
